Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-23 docs/supplementary_material.tex
conditional fonts

\usepackage{lineno}
\setmainfont{Times New Roman}
\setsansfont{Arial}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}
  \KeywordTok{readLines}\NormalTok{(}
    \DataTypeTok{con =} \StringTok{"data/model\_output\_residence\_patch.txt"}
\NormalTok{  ), }\DataTypeTok{sep =} \StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

\usepackage{lineno}

\IfFontExistsTF{Times New Roman}{\setmainfont[]{Times New Roman}}{} 
\IfFontExistsTF{Arial}{\setsansfont[]{Arial}}{}
\IfFontExistsTF{Fira Code}{\setmonofont{Fira Code}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}
  \KeywordTok{readLines}\NormalTok{(}
    \DataTypeTok{con =} \StringTok{"data/model\_output\_residence\_patch.txt"}\NormalTok{,}
    \DataTypeTok{encoding =} \StringTok{"UTF{-}8"}
\NormalTok{  ), }\DataTypeTok{sep =} \StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}
\NormalTok{)}
\CommentTok{\#> }
\CommentTok{\#> Call:}
\CommentTok{\#> lm(formula = duration\_real \textasciitilde{} duration, data = patch\_summary\_compare)}
\CommentTok{\#> }
\CommentTok{\#> Residuals:}
\CommentTok{\#>      Min       1Q   Median       3Q      Max }
\CommentTok{\#> {-}103.237  {-}19.277   {-}2.917    7.003   93.431 }
\CommentTok{\#> }
\CommentTok{\#> Coefficients:}
\CommentTok{\#>              Estimate Std. Error t value Pr(>|t|)    }
\CommentTok{\#> (Intercept) 101.42061   47.66936   2.128   0.0493 *  }
\CommentTok{\#> duration      1.02108    0.07876  12.965 6.66e{-}10 ***}
\CommentTok{\#> {-}{-}{-}}
\CommentTok{\#> Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
\CommentTok{\#> }
\CommentTok{\#> Residual standard error: 50.35 on 16 degrees of freedom}
\CommentTok{\#> Multiple R{-}squared:  0.9131,	Adjusted R{-}squared:  0.9077 }
\CommentTok{\#> F{-}statistic: 168.1 on 1 and 16 DF,  p{-}value: 6.655e{-}10}
\end{Highlighting}
\end{Shaded}
